Efficient Coalition Formation \\ for Web Services

### 2013-07-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings. The idea of grouping
web services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar
functionalities, but probably different non-functional quality
attributes, which form the QoS parameters. When communities are
used, users send their requests to the masters of those
communities, which are responsible of managing the communities,
forwarding the requests to the suitable member web services and
checking the credentials of those members. Communities aim to
provide higher service availability and performance than what
individual web services can provide. The high availability of
services and the community resilience to failure are guaranteed
since web services can cooperate and replace each other within the
same community and since there is no single point of failure in
the communities architecture.

@@

In \cite{10.1109/TSC.2012.12} a cooperative scheme among autonomous 
web services based on coalitional game theory has been introduced. They have proposed an algorithm to 
reach individually stable coalition partition for web services in order to
maximize their efficiency. The communities choose new web services on the promise 
that no it would benefit the community without decreasing any other web service's
income. In their model, the worth of community is evaluated with a lot of emphasis on 
availability metric and also considering price and cost values only. The community structure is based on a coordination chain,
where a web service is assigned as a \emph{primary} web service and the community task destribution
method, will initially invoke primary web service and only if the primary web service is unavailable
will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to 
have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays 
with recent advancement in cloud and hardware infrastructures availability is less of an issue. So the backup web services 
in their model have a very low chance of getting jobs, especially the ones further in chain which is huge waste of web service
capability.

@@

The rest of paper is organized as follows. Section
\ref{s:preliminaries} describes the architecture, considered
parameters and some basic cooperative game theory concepts.
Section \ref{s:model} presents our solution model in three
different scenarios. Section \ref{s:resutls} describes our
experiments and results. Finally, Section \ref{s:conclusion},
concludes the paper and identifies future work.

@@

Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition Method} because of nature of their community valuation function, which considers community availability as main consideration. Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible. We limited our maximum community size by 5 in order to have communities with almost the same size. In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task. However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available. Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Method} because of real cooperative nature and task distribution of our algorithm. This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work. The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}. Part(c) shows the availability of community from end user point of view. The \emph {High Availability Method} almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase. In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.

>>>>

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings. The idea of grouping
web services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar
functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,Liris-3375}, but probably different non-functional quality
attributes, which form the QoS parameters. When communities are
used, users send their requests to the masters of those
communities, which are responsible of managing the communities,
forwarding the requests to the suitable member web services and
checking the credentials of those members. Communities aim to
provide higher service availability and performance than what
individual web services can provide. The high availability of
services and the community resilience to failure are guaranteed
since web services can cooperate and replace each other within the
same community and since there is no single point of failure in
the communities architecture.

@@

In \cite{10.1109/TSC.2012.12} a cooperative scheme among autonomous 
web services based on coalitional game theory has been introduced. They have proposed an algorithm to 
reach individually stable coalition partition for web services in order to
maximize their efficiency. The communities choose new web services on the promise 
that it would benefit the community without decreasing any other web service's
income. In their model, the worth of community is evaluated with high emphasis on 
availability metric and considering price and cost values only. The community structure is based on a coordination chain,
where a web service is assigned as a \emph{primary} web service and the community task destribution
method, will initially invoke the primary web service and only if the primary web service is unavailable
will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to 
have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays 
with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services 
in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
capabilities.

@@

The rest of paper is organized as follows. Section
\ref{s:preliminaries} describes the architecture, considered
parameters and some basic cooperative game theory concepts. 
Section \ref{s:model} provides the problem statement and some numerical examples.
Section \ref{s:game_solution} presents our solution model in two
different scenarios. Section \ref{s:resutls} describes our
experiments and results. Finally, Section \ref{s:conclusion},
concludes the paper and identifies future work.

@@

Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition} method, because of nature of their community valuation function, which focuses on community availability as main consideration. Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible. We limited our maximum community size by 5 in order to have communities with almost the same size. In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task. However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available. Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Coalition} method because of real cooperative nature and task distribution of our algorithm. This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work. The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}. Part(c) shows the availability of community from end user point of view. The \emph {High Availability Coalition} method almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase. In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.
